---
title: "Linguistic Alignment and Collaborative Problem-Solving in Online and Team-Based Interactions - SPLIT-LEVEL ALL BLOCKS"
author: "Nick Duran"
date: 10/14/21
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

```{r}
library(tidyverse)
library(pander)
```


```{r}
# **person.csv contains the following which is most relevant for us**:
#   + see: https://docs.google.com/document/d/1ihz2GNXj3g9yaopu1xGD-7x9CEW9qwwCRkWE98o_9rM/edit#

person = read.csv('Accompanying_Data/Step2_FilesToIntegrate/person.csv', sep=",") 
person = person %>% mutate(School = word(userID, 2, sep="-"), Team = word(userID, 3, sep="-"), participant = word(userID, 4, sep="-")) %>%
  select(-userID)
person = person %>% select(c(2, 57, 1, 58, 59, everything()), -school) %>% rename(School_Team = "team")

```

### Group Makeup / Group Level

> **demographics** are one-hot encoded:

  * isMale
  * isFemale
  * isOtherGender

> **Big Five (Personality) Measures**, summed across the two items in the survey:

  * extraversion
  * agreeableness
  * conscientiousness
  * stability
  * openness

```{r}
# let's start with creating the gender classification for each team
gendem = person %>% 
  group_by(School_Team) %>% 
  mutate(samegen = ifelse(sum(isFemale) == 3 | sum(isMale) == 3, 1, 0)) %>%
  mutate(femdom = ifelse(sum(isFemale) >= 2, 1, 0)) %>%
  dplyr::summarize(samegend = mean(samegen), femdomin = mean(femdom)) %>% 
  ungroup()
```

```{r}
# now, let's create a vector of the big five dimensions for each participant within a team and compute the Euclidean distance 
# to do this, let's split the userID column to identify each unique participant [might not be necessary at all]
# next, group by team and then create the vector
# next, compute Euclidean between each pair (three pairs in total) and then get the average score

# ok resource for doing this:
# https://cran.r-project.org/web/packages/philentropy/vignettes/Distances.html

rcols = c("extraversion", "agreeableness", "conscientiousness", "stability", "openness")
persDiv = c()
School_Team = c()
for (i in 1:nrow(person)-1) {
  if (i > 1 && person$School_Team[i] == person$School_Team[i-1] && person$School_Team[i] == person$School_Team[i+1]) {
    matrixbuild = c()
    
    matrixbuild = as.matrix(person[i,rcols]) 
    matrixbuild = rbind(matrixbuild, as.matrix(person[i-1,rcols]))
    matrixbuild = rbind(matrixbuild, as.matrix(person[i+1,rcols]))
    distPer = mean(stats::dist(matrixbuild, method = "euclidean")) 
    
    persDiv = c(persDiv, distPer)
    School_Team = c(School_Team, as.character(person$School_Team[i]))
  }
}
persDivDF = data.frame(School_Team, persDiv)
persDivDF = persDivDF

```

### Individual Scores

  * PhysicsScorePre
  * PhysicsScorePost
  * race_value
  * ISWT_collectivism_mean: individual satisfaction with the team collectivism measure
  * Lead_ISWT_self_efficacy_mean: self-efficacy for leadership measure combined with individual satisfaction with the team teamwork self-efficacy measure b/c the two were highly correlated. To combine, first z-score the two measures individually and then take the mean
  * SEP_mean: mean of self-efficacy for physics measures
  * IMI_PP_interest_enjoyment_mean
  * IMI_PP_perceived_competance_mean
  * IMI_PP_effort_importance_mean
  * IMI_PP_pressure_tension_mean
  * IMI_PP_value_usefulness_mean 

```{r}
individ_measures1 = person %>% select(School_Team, School, Team, participant, PhysicsScorePre, PhysicsScorePost, raceValue, ISWT_collectivism_mean, Lead_ISWT_self_efficacy_mean,
                                      SEP_mean, IMI_PP_interest_enjoyment_mean, IMI_PP_perceived_competance_mean, 
                                      IMI_PP_effort_importance_mean, IMI_PP_pressure_tension_mean, IMI_PP_value_usefulness_mean)
```

  * CPS_and_ITN_mean
  * XQ_know

```{r}
# **person_block.csv contains the following which is most relevant for us**:
#   + see: https://docs.google.com/document/d/1ihz2GNXj3g9yaopu1xGD-7x9CEW9qwwCRkWE98o_9rM/edit#

personblock = read.csv('Accompanying_Data/Step2_FilesToIntegrate/person_block.csv', sep=",")
personblock = personblock %>% mutate(School = word(userID, 2, sep="-"), Team = word(userID, 3, sep="-"), participant = word(userID, 4, sep="-")) %>%
  select(-userID)
individ_measures2 = personblock %>% select(c(2, 26, 1, 3, 27, 28, 10, 18, -school)) %>% rename(School_Team = "team") %>% filter(Block == "Transfer") %>% select(-Block)
```

### Create Master

> the additional variables in one place

```{r}
master1 = left_join(individ_measures1,individ_measures2)
master2 = left_join(master1, persDivDF)
master3 = left_join(master2, gendem)
```

> now add to the main dataset

```{r}
master3 = master3 %>% select(-School_Team) %>% rename(aligner_score = "participant")

compositeLing_role = read.csv("Data/Step1_PrepareFeatures.csv", header=TRUE, sep=",")

compositeLing_role =  left_join(compositeLing_role, master3)
write.csv(compositeLing_role, "Data/Step2_Optional_IndividDiff.csv", row.names=FALSE)

```






<!-- #### Block-level performance ONLY RELEVANT FOR CODING SCHEME 1 BLOCK LEVEL VARIABLES -->

```{r}
# **CPS facets** 
#   Construction of Shared Knowledge
#   Negotiation/Coordination
#   Maintaining Team Function
 
# **Objective Performance Scores**
#   Prop_Gold_Trophies: proportion of the gold trophies they earned in that block; note the max possible number of trophies varies by EcT vs PoT
#   Prop_Silver_Trophies: proportion of the silver trophies they earned in that block; note the max possible number of trophies varies by EcT vs PoT
#   Prop_Unique_Trophies: proportion of trophies they earned in that block; note the max possible number of trophies varies by EcT vs PoT
 
## ADD THESE FOR FIRST ANALYSIS WHERE CODES WERE DONE AT THE BLOCK RATHER THAN SPLIT LEVELS
# block_level = personblock %>% select(c(2, 26, 1, 3, 27, 28, COMM, NEG, MAINTAIN, Prop_Gold_Trophies, Prop_Silver_Trophies, Prop_Unique_Trophies, -school)) %>% rename(School_Team = "team") %>% filter(Block != "Transfer")
```




















