---
title: "Multi-Level Linguistic Alignment in a Dynamic CPS Tasks: Step 3 Model 1"
author: "Nick Duran"
date: 10/14/21
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# rm(list=ls())
```

> Notebook contains code for replicating section in manuscript: Analysis 1: Alignment over time

### Step 1: Import main data file and run script to prep variables for analysis

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(tidyverse)
library(pander)
```

```{r}
main.data = read.csv("../Data/Step1_PrepareFeatures.csv")

# test1 = main.data %>%
#   group_by(Team, School, Block, Level, revisited) %>%
#   filter(n() >= 20) %>%
#   ungroup()
#   
# ## remove extraordinarily long single utterances (removes 282 rows, or (282/34294)*100, or less than 1%)
# ## why 71? Because this is 5SDs above mean of utterlen: mean(main.data$utterlen_aligner)+(5*sd(main.data$utterlen_aligner))
# test2 = test1 %>% filter(utterlen_aligner < 71 & utterlen_target < 71)

source("../R_Helper/Step3_helper.R")
main.data.20 = variable_prep(main.data)

pander(names(main.data.20))
# head(main.data.20)
```

* Relies heavily on "Step3_helper.R." This code does the following:

  * remove levels that are fewer than 20 turns
  * Convert # of turns to a running proportion score 
  * Get z-scores for relevant variables
  * create ordered factor for block (interested in linear trend)
  * create random factor for within subject variance (making sure each unique subject is signified given their school and team)

### Step 2: Check the distributions of the main outcome linguistic variables

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(DataExplorer)

g1 = main.data.20 %>% select(lexical, syntax, semantic)
plot_histogram(g1)
```

The outcome variables of lexical and syntactic is clearly distribute with clumping at zero (hurdle, bounded) with a skew in the positive values (unbounded, gamma), As such, what is required is the use of zero-inflated gamma models, i.e., gamma hurdle models; zero-altered gamma models; two-part models (a binomial model for predicting occurrence of nonzero, a second [linear model (or Gamma, or truncated Normal, or log-Normal)] for evaluating the relationship of nonzero value to predictors)

### Step 3: Build zero-inflated gamma models: LEXICAL

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(glmmTMB)
library(parameters) 

library(strengejacke)
```

#### glmmTMB approach

To start, going to build with a glmmTMB model that allows random effect structure. We are going to use the gamma distribution because we are dealing with non-integer (non-count) data as our DV and thus is continuously distributed, with some skew in the positive direction. Starting with the simplest random effect structure model with subject. 

<!-- Going to use a ziGamma model for overdisperion, but is there a way to check for this?  -->
<!-- truncated_nbinom2 instead of ziGamma? -->

```{r}
# zigamma_lex <- glmmTMB(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1|subject_id),
#                          family = ziGamma(link = "log"), #gamma because deling with non-integer counts
#                          ziformula = ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1|subject_id), 
#                          data = main.data.20)
```

```{r}
# summary(zigamma_lex)
```

The initial summary shows that subject-level variance is incredibly small. 

What about a more complex random effects structure? Would this improve variance accounted for at subject-level? Attempting two more models with theoretically-plausible structures and will compare all models with an AIC test for selection. 

[Note: I have also attempted to run models with "Level" but does not converge. And a model with "(ordering_prop|subject_id) + (Block.l|subject_id)" does not converge]. 

```{r}
zigamma_lex2 <- glmmTMB(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (aligner_role|subject_id),
                         family = ziGamma(link = "log"), 
                         ziformula = ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (aligner_role|subject_id),
                         data = main.data.20)
```

```{r}
# summary(zigamma_lex2)
```

```{r}
# zigamma_lex3 <- glmmTMB(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (ordering_prop|subject_id),
#                          family = ziGamma(link = "log"),
#                          ziformula = ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (ordering_prop|subject_id), 
#                          data = main.data.20)
```

```{r}
# summary(zigamma_lex3)
```

```{r}
## Did not converge

# zigamma_lex4 <- glmmTMB(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1+aligner_role|subject_id) + (0+ordering_prop|subject_id),
#                          family = ziGamma(link = "log"),
#                          ziformula = ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1+aligner_role|subject_id) + (0+ordering_prop|subject_id),
#                          data = main.data.20)
#
```

```{r}
# summary(zigamma_lex4)
# # tab_model(zigamma_lex4)
```

To compare models, use ‘bbmle’. See: https://journal.r-project.org/archive/2017/RJ-2017-066/RJ-2017-066.pdf, page 381: use the  AICtab function. Best resources for doing a comparison is with: 
https://www.ashander.info/posts/2015/10/model-selection-glms-aic-what-to-report/
http://ms.mcmaster.ca/~bolker/R/misc/foxchapter/bolker_chap.html

What we're looking for is the highest weighted model. 

```{r}
# model.names <- c("1 Subject", "2 Subject + Aligner Role", "3 Subject + Ordering")
# reported.table1 <- bbmle::AICtab(zigamma_lex, zigamma_lex2, zigamma_lex3, weights = TRUE, sort = FALSE, mnames = model.names)
# reported.table1
```

Although a mixed effects models with a role|aligner effects structure is best, the random effect structure is still incredibly small. 

```{r}
VarCorr(zigamma_lex2)
```

#### glm and glmer approach (explicitly run two separate models)

For comparison, we can also explicitly fit (non-mixed) generalized linear models with complete pooling of subject. Here, we fit separately the conditional and zero-inflated model. We use the method outlined here: https://seananderson.ca/2014/05/18/gamma-hurdle/. 

```{r}
main.data.20.separate = main.data.20 %>% mutate(non_zero_lex = ifelse(lexical > 0, 1, 0))
```

```{r}
## zero-inflated binomial model
z1.glm <- glm(non_zero_lex ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept, data = main.data.20.separate, family = binomial(link = logit))

## NOTE: was getting an warning that "Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred" ; but this appears to be an issue because there were  extreme outliers for utterance length of some rows. Removed these outliers (.80% of data) and now no issue with model. Used this to resolve: https://stats.stackexchange.com/questions/336424/issue-with-complete-separation-in-logistic-regression-in-r https://stats.stackexchange.com/questions/396008/glm-fit-fitted-probabilities-numerically-0-or-1-occurred-however-culprit-featur
```

```{r}
summary(z1.glm)
# tab_model(z1.glm)
```

```{r}
## linear gamma model
g1.glm <- glm(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept, data = subset(main.data.20.separate, non_zero_lex == 1), family = Gamma(link = log))
```

```{r}
summary(g1.glm)
# tab_model(g1.glm)
```

The results are very similar, if not essentially identical. 

Is there a preferred one to use? One way is to compare models with and without random effects. To do that, need to separate out the models for the zero-inflated and gamma components as did with GLM. But now with GLMER. 

```{r}
library(lme4)
# library(aods3)

z1.glmer1 <- lme4::glmer(non_zero_lex ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1|subject_id), data = main.data.20.separate, family = binomial)

g1.glmer1 <- lme4::glmer(lexical ~ ordering_prop + Block.l + aligner_role + relative_start_timeZ + level_durationZ + utterlen_alignerZ + Concept + (1|subject_id), data = subset(main.data.20.separate, non_zero_lex == 1), family = Gamma(link = log))
```

Now compare, and it looks like the random effects structure model wins out. 

```{r}
reported.table2 <- bbmle::AICtab(z1.glm, z1.glmer, weights = TRUE, sort = FALSE)
reported.table2

reported.table3 <- bbmle::AICtab(g1.glm, g1.glmer, weights = TRUE, sort = FALSE)
reported.table3
```

#### Issue w/ checking over-dispersion

We can also check for over-dispersion to help justify the gamma distribution if we wanted. The description for how to do this can be found in these resources:
http://ms.mcmaster.ca/~bolker/R/misc/foxchapter/bolker_chap.html

The problem is that the easy function for checking (aods3:gof) does not work with glmmTMB (zigamma_lex2). So, just using g1.glmer. But really, it is clearly over-dispersed and using the gamma distribution makes sense. 

Check the GLM model:

```{r}
gof(g1.glm)
```

Check the GLMER model:

```{r}
gof(g1.glmer)
```

### Conclusion

Let's use the random effects structure model acknowledging that very little variance is explained at the subject/role level. 

At this point, we can say the following, based on some of the suggested write-up in the Boker chapter and elsewhere:

<!-- For interpreting the intercept, the mean value (model adjusted on log-scale) of lexical is 0.26 -->

```{r}
# confint(zigamma_lex2,method="Wald")
```

```{r}
# exp(confint(zigamma_lex2,method="Wald"))
```

```{r}
VarCorr(zigamma_lex2)
```

```{r}
tab_model(zigamma_lex2, transform=NULL, digits=3, show.zeroinf=TRUE, digits.re = 4)
```


Analytical Strategy:


A gamma distribution that accounts for overdispersion...  

Prevalance and degree of alignment. 

Multilevel gamma hurdle model (MGH). They allow the specification of distinct probability functions for observations where y=0, and y>0. That is, examines the probability of observing a zero count, and if the hurdle is crossed (if y>0), then we examine the truncated density. 

Binary model. 

An advantage of the hurdle model is that its components (the prevalence and truncated models) can be estimated separately (independently). 

"However, when observations are clustered and random effects are used, as in the multilevel approach used here, the two stage estimation procedure assumes that group random effects for prevalence and concentration are independent, when in fact they may be correlated." 

All models were estimated using the "glmmTMB" package. 

"We estimated the standard MNB model as a baseline to compare the estimates of the MNB-LH model.

"For count MNB and MTNB models, the exponentiated estimates represent incidence rate ratios (IRR, Hilbe 2014, p. 60), whereas for the binary ML model they represent odds ratios (OR, Weisburd and Britt 2014, p. 568). Subtracting 1 from the IRR (𝐼𝑅𝑅−1) gives the percentage change on the concentration of extortion victimization for a one unit increase in the independent variable, while 𝑂𝑅−1 gives the percentage change in the prevalence risk. For categorical independent variables, the percentage change is relative to the reference category."




Zero-inflated model:
For predicting the likelihood of zero alignment as conversational turns progress in a level, there was no statistically significant difference over time (log effect estimate = 0.021, Wald CI: { }). However, at the broader scale, when collapsed across rounds, the later rounds showed a higher incidence of zero alignment, with an approximately 7.11% (log effect estimate: ) increase of zero values (Wald CI: { }). The estimate of participant-level variance, taking into account role as a controller or observer, was ..., indicating very little variation among subjects, with a 95% Wald CI of { }.   

Conditional model:
For the conditional model based on the distribution of lexical alignment values greater than zero, a	1 unit increase at the scale of	turn order (from the start to end of the level)	was	associated with a 2.93% reduction (log effect estimate: -0.030) in the mean of lexical alignment (95% Wald CI={}). The change over the larger scale of rounds was not statistically significant (log effect estimate = 0.021, 95% Wald CI={}). The among-subject standard deviation was again small, at ..., with a 95% Wald CI of { }.  

The statistical significance for the co-variates in the zero-inflated and conditional models were very similar. For the zero-inflated model (likelihood of zero lexical alignment vs any lexical alignment), ...  

For the distribution of lexical alignment of values greater than zero, ... 



```{r}
summary(zigamma_lex2)
```





any lexical alignment (values greater than 0), there was no change of likelihood as turns progressed within an level. That is, the odds of there being no alignment based on turn position was not statistically significantly different than there being alignment. But over the larger scale of rounds (linear trend from 1st to 3rd round), the odds of there being no lexical alignment increased by 7.11% (log effect estimate: -0.030). That is, there was an 7.11% increase in having no occurrence of lexical alignment by the final round.   



	“A	1%	increase	in	
seroprevalence	was	associated	with	an	approximately	2.1%	increase	(log	effect	
estimate=0.021)	in	the	density	of	fresh	shells	(95%	CI={0.013,0.031}	by	parametric	
bootstrap	[PB]).	Both	of	the	years	subsequent	to	2004	had	lower	shell	densities	(logdifference	=-0.64	(2005),	-0.43	(2006)),	but	the	differences	were	not	statistically	
significant	(95%	PB	CI:	2005={1.34,0.05},	2006={-1.04,0.18}).	There	was	no	detectable	
overdispersion	(Pearson	squared	residuals/residual	df=0.85;	estimated	variance	of	an	
among-observation	random	effect	was	zero).	The	best	estimate	of	among-site	standard	
deviation	was	zero,	indicating	no	discernable	variation	among	sites,	with	a	95%	PB	CI	of	
{0,0.38}.”













For the **linear component (gamma)** component, assuming a non-zero value, a 1 unit increase in ordering_prop (from the start [0] to the end [1]) leads to a 0.97 decrease in the mean of lexical. Put in another way, increasing ordering_prop 0 to 1 (start to finish) causes a 2.93% (1-(exp(-0.0297724))) * 100 reduction in the mean amount of lexical alignment. Or, we can change the unit size to .10 increments. If so, increasing ordering_prop by 1/10 increments causes a 0.30% (1-exp(-0.0297724 * 0.1)) * 100 reduction in the mean amount of lexical.

For the **binomial component** predicting whether lexical alignment occurred at all, although no change of likelihood across a level, for likelihood across blocks, the odds of there being no lexical alignment increased by 1.07 times exp(0.0686873). That is, there was an 7.11% increase in having no occurrence of lexical alignment by the final round.


#### How to interpret (generally): 

For the **linear component (gamma)**, we use a log link that allows us to predict the model-adjusted mean of the non-zero data on the log scale. Being on the log scale, we can also exponentiate to make claims about how a unit increase in response value x leads to a probabilistic decrease or increase in the mean of the outcome. For example: A 1 unit increase in x leads to a 0.012 decrease in the mean of the outcome. Put another way, increasing x by 1 causes a 98.8% reduction in the predictor. 

For the **binomial component** we use a logit link to predict "0" (nonoccurrence) and then exponentiate the resulting coefficient to report the probability of seeing a nonoccurrence. 


################################################

```{r}
model_parameters(zigamma_lex2, exponentiate = T)
```

Show the model parameters in a cleaner format

```{r, warning=FALSE, message=FALSE, error=FALSE}
tab_model(zigamma_lex
          # show.intercept = FALSE,
          # show.r2 = TRUE,
          # show.icc = FALSE,
          # show.re.var = FALSE,
          # show.ngroups = FALSE,
          # show.obs = FALSE,
          # string.est = "Incidence Rate Ratios"
          )
```








Ok, new notes from 11/19/21:

A very good paper for just talking about the random effect structure of LMER models, ensures that what is being reported is accurate and gives a critical citation: http://www.singmann.org/download/publications/singmann_kellen-introduction-mixed-models.pdf

An interesting discussion of how to determine whether the random effects variables are worth including, whether a mixed effects model is even necessary. Brings up the interesting idea of using models with and without the effect and comparing with AIC
https://stats.stackexchange.com/questions/56150/how-can-i-test-whether-a-random-effect-is-significant

In one of the responses to the main thread, a very good point that "although there is 'obviously' variation in subject performance, the extent of this subject variation can be fully or virtually-fully explained by just the residual variance term alone. There is not enough additional subject-level variation to warrant adding an additional subject-level random effect to explain all the observed variation."
https://stats.stackexchange.com/questions/115090/why-do-i-get-zero-variance-of-a-random-effect-in-my-mixed-model-despite-some-va

Not the greatest post, but makes the point that gamma works on continuous non-negative distributions, whereas poisson and negative binomial do not:
https://timothy-barry.github.io/posts/2020-06-16-gamma-poisson-nb/

********Topic: Overdispersion
Not sure whether I need to explicity test for this or not, as visually, it appears to be overdispersed. However, need to plot the residuals to know for sure. So, strike previous comment. Cannot merely plot the DV to make a determination. 
Just ok resources but useable to back up some claims. 
https://biometry.github.io/APES/LectureNotes/2016-JAGS/Overdispersion/OverdispersionJAGS.pdf
https://biometry.github.io/APES//LectureNotes/2016-JAGS/Overdispersion/OverdispersionJAGS.html

*******Topic: "How to model non-negative zero-inflated continuous data?"
Given this is exactly what I'm trying to do, this thread was helpful and pointed to the need of running zero-inflated/hurdle models (i.e., two-part models) 
https://stats.stackexchange.com/questions/187824/how-to-model-non-negative-zero-inflated-continuous-data

But this post also suggests running a model where you run the two parts yourself rather than relying on a single function, like glmmTMB, especially if I want to build a model without the random effects structure. This tutorial shows you how:
https://seananderson.ca/2014/05/18/gamma-hurdle/

This seananderson paper is really useful as it does make the points that most packages are built for count data (and he lists a bunch of these options), but this doesn't help me much. He also reinforces the point that what is needed are binomial-Gamma hurdle models. 

Use this paper when citing glmmTMB models:
https://journal.r-project.org/archive/2017/RJ-2017-066/RJ-2017-066.pdf









